### 2013-12-02 manuscripts/reply/short-reply.tex
opening paragraphs

\newpage
\citet{}

\msb
\citep{Huang2011} uses approximate Bayesian computation (ABC) to
estimate the temporal distribution of divergences among co-distributed pairs of
taxa by sampling over models of divergence that range from a single
divergence-time parameter (i.e., all pairs of taxa diverged at the same time)
to the fully generalized model in which each pair is assigned a divergence-time
parameter.
A full description of the model is given in \citet{Oaks2012}.

\citet{Oaks2012} published results of simulation-based power analyses showing
that \msb is biased toward inferring models of temporally clustered divergence
times across taxon pairs.
\citet{Hickerson2013} published a response to \citet{Oaks2012} where they
present an empirical Bayesian model-averaging approach that they conclude
circumvents the problems revealed by \citet{Oaks2012}.
These papers are largely in agreement, with \citet{Hickerson2013} reiterating
much of the discussion of \citet{Oaks2012} regarding the impact of broad
uniform priors on Bayesian model choice.
Both papers agree that when broad uniform priors are used to reflect \emph{a
prior} uncertainty about divergence times of all pairs of taxa under study,
the method can be biased toward inferring biogeographically interesting
scenarios of temporally clustered divergences among taxa (i.e. models with few
divergence-time parameters).
Both papers also agree that this bias toward models with few divergence-time
parameters is due to the much greater parameter space of models with more
divergence-time parameters.
However, the papers disgree about the primary mechanism by which the greater
parameter space of parameter-rich models causes the bias toward clustered
divergence models;
\citet{Oaks2012} suggest a statistical issue is the cause, whereas
\citep{Hickerson2013} prefer a numerical explanation.
% The main areas of disagreement between the papers are centered around
% (1) the mechanism by which broad uniform priors cause the bias of \msb toward
% models with few divergence-time parameters, and
% (2) how to potentially mitigate this issue.

\citet{Oaks2012} suggest the primary cause of the bias of \msb is the low
marginal likelihoods of parameter-rich models integrated over vast parameter
space with low probability of producing the data, yet relatively high prior
density \citep{Lindley1957} imposed by the uniformly distributed prior on
divergence times.
Note, this suggests the bias is extrinsic to \msb, and the numerical
approximation machinery of \msb could be sound.
\citet{Hickerson2013} suggest the bias is intrinsic to \msb, concluding the
method's rejection algorithm is inefficient and will be biased
toward models with fewer divergence-time parameters, because the parameter
space of these models are more densely sampled relative to models with more
divergence-time parameters.
We agree that sampling error is present in all numerical Bayesian estimation
methods, however, we show here that it is not a major contributer to the
biases found by \citet{Oaks2012}.
We present results of additional analyses that, when combined with
the results of \citet{Oaks2012}, strongly suggest small marginal likelihoods of
models with more parameter space is a primary mechanism by which uniform priors
are causing the bias of \msb.

>>>>

\newpage
\msb
\citep{Huang2011} uses approximate Bayesian computation (ABC) to
estimate the distribution of divergence times among co-distributed pairs of
taxa.
It approximates a posterior probability over models that range from a single
divergence-time parameter (i.e., simultaneous divergence of all pairs of taxa)
to the fully generalized model in which each pair of taxa diverged at a
unique time.
A full description of the model is given in \citet{Oaks2012}.
Frequently, the exact value of the divergence times are hard 
to determine because researchers typically lack precise knowledge 
of the rate at which substitutions occur.
So the exact divergence time is often viewed as a nuisance parameter, and
researchers focus on the number of divergence events.
The papers of \citet{Oaks2012} and \citet{Hickerson2013} are in agreement
on the fundamental methodological point about the model selection performed in \msb:
\begin{itemize}
   \item the use of vague priors on the divergence time parameters can 
    lead to support models with few divergence time events. Thus, the 
    primary inference enabled by the approach is very sensitive to the
    priors on divergence times.
\end{itemize}

\citet{Oaks2012} suggest that primary cause of the bias of \msb is the low
marginal likelihoods of parameter-rich models integrated over vast parameter
space with low probability of producing the data, yet relatively high prior
density \citep{Lindley1957} imposed by the uniformly distributed prior on
divergence times.
Note, this suggests the bias is extrinsic to \msb, and the numerical
approximation machinery of \msb could be sound.
\citet{Hickerson2013} suggest the bias is intrinsic to \msb, concluding the
method's rejection algorithm is inefficient and will be biased
toward models with fewer divergence-time parameters, because the parameter
space of these models are more densely sampled relative to models with more
divergence-time parameters.
We agree that sampling error is present in all numerical Bayesian estimation
methods, however, we show here that it is not a major contributer to the
biases found by \citet{Oaks2012}.
We present results of additional analyses that, when combined with
the results of \citet{Oaks2012}, strongly suggest small marginal likelihoods of
models with more parameter space is a primary mechanism by which uniform priors
are causing the bias of \msb.
